\subsection{Attacking Enemy Hills and Ants}
Attacking is a hard and very important problem for the bot. Given the grid-based movement, we must rely on very precise collaboration of two or more ants in order to carry out a successful attack. We must have at least two ants attacking a single enemy ant simultaneously in order to avoid sacrificing an ant. Sacrificing ants is certainly an option, but it is associated with defense, not offence.

Correctly placing ants around an enemy ant, in order to attack it, requires precise timing. Furthermore it involves some prediction of the enemy ant's future movement. As ants can attack each other within a given radius (read circle), we cannot guarantee sacrificing one for one when attacking with just two ants. We can prevent losses in 3 of 4 cases of enemy ant movement. Using three ants in an attack, we can ensure no losses of our own, yet there is still the possibility of the enemy ant fleeing. All of this requires that only one enemy ant is within attack radius. This is mostly fine, as an attack on a single enemy ant is likely due to collecting food, otherwise we will be attacking an enemy hill which obviously cannot move.

Attacks require a number of ants doing basically the same thing for a number of turns. During this time, these ants will not be collecting food, thus reproducing further ants. This makes it hard to determine when an attack is appropriate, and just as important, which ants to use. As the game goes on and the density of ants increase this quickly becomes a complex and time-consuming problem to solve. For the current version of the bot, we rely on only looking at a small subset of closely located ants in order to carry out an attack. We are not yet sure how to prioritize attacks vs. finding food or exploring the map. 